Testing d3

### 2023-01-11 text/20/ihme-model.Rmd

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: "New"
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

>>>>

---
title: "Criticisms of the IHME COVID-19 model"
author: "Steve Simon"
source: new
date: 2020-04-23
categories:
- Blog post
tags:
- Epidemiology
output: html_document
---

### 2023-01-11 text/20/map-projections.Rmd

---
title: "Blog post: Different map projections"
author: "Steve Simon"
source: "New"
date: "2020-03-15"
category: Blog post
tags: Graphical display
output: html_document
---

>>>>

---
title: "Different map projections"
author: "Steve Simon"
source: new
date: "2020-03-15"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---
install.packages("rnaturalearthhires", repos="http://packages.ropensci.org", type="source")

### 2023-01-11 text/20/poor-color-chioce.Rmd

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: "New"
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "An example of a poor color choice"
author: "Steve Simon"
source: new
date: "2020-03-11"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

### 2023-01-11 text/20/reading-text-files.Rmd

---
title: "Reading text files"
author: "Steve Simon"
source: "New"
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: "Reading text files"
author: "Steve Simon"
source: new
date: "2020-04-30"
categories:
- Blog post
tags:
- Data management
output: html_document
---

### 2023-01-11 text/20/rmarkdown-papers.Rmd

---
title: "How I use R Markdown to write research papers"
source: "New"
date: "2020-11-21"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---

>>>>

---
title: "How I use R Markdown to write research papers"
source: new
date: "2020-11-21"
categories:
- Blog post
tags:
- Writing research papers
output: html_document
---

### 2023-01-11 text/20/smart-quotes.Rmd

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
---

>>>>

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: new
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
---

### 2023-01-11 text/21/anonymizing-ids.Rmd

---
title: "Anonymizing ids"
author: "Steve Simon"
source: "New"
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

>>>>

---
title: "Anonymizing ids"
author: "Steve Simon"
source: new
date: "2021-06-10"
categories:
- Blog post
tags:
- Privacy in research
output: html_document
---

### 2023-01-11 text/21/dark-side.Rmd

---
title: "The dark side of big data"
source: "New"
date: "2021-10-28"
categories:
- Blog post
tags:
- Data science
- Incomplete page
output: html_document
---

>>>>

---
title: "The dark side of big data"
source: new
date: "2021-10-28"
categories:
- Blog post
tags:
- Data science
- Incomplete page
output: html_document
---

### 2023-01-11 text/21/glm-deviance.Rmd

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: "New"
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Deviance in a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

### 2023-01-11 text/21/glm-diagnostics.Rmd

---
title: "Diagnostics for a generalized linear model"
author: "Steve Simon"
source: "New"
date: "2021-10-18"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Diagnostics for a generalized linear model"
author: "Steve Simon"
source: new
date: "2021-10-18"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

### 2023-01-11 text/21/hurricane-frequencies.Rmd

---
title: "Overfitting example using hurricane frequencies"
author: "Steve Simon"
source: "New"
date: "2021-12-11"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Overfitting example using hurricane frequencies"
author: "Steve Simon"
source: new
date: "2021-12-11"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

### 2023-01-11 text/21/negative-binomial-regression.Rmd

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: "New"
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
output: html_document
---

>>>>

---
title: "Working with negative binomial regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
- Generalized linear model
output: html_document
---

### 2023-01-11 text/21/poisson-regression.Rmd

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: "New"
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with Poisson regression"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

### 2023-01-11 text/21/quasi-likelihood.Rmd

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: "New"
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

>>>>

---
title: "Quasi-likelihood models"
author: "Steve Simon"
source: new
date: "2021-09-20"
categories:
- Blog post
tags:
- Generalized linear model
output: html_document
---

### 2023-01-11 text/21/read-acs-data.Rmd

---
title: "Reading information from the American Community Survey into R"
source: "New"
date: "2021-09-29"
categories:
- Recommendation
tags:
- Website details
output: html_document
---

>>>>

---
title: "Reading information from the American Community Survey into R"
source: new
date: "2021-09-29"
categories:
- Recommendation
tags:
- Website details
output: html_document
---

### 2023-01-11 text/22/testing-d3.Rmd

---
title: "Testing d3"
author: "Steve Simon"
date: "2022-06-01"
source: "New"
categories: 
- Blog post
tags: 
- Graphical display
output: html_document
---

>>>>

---
title: "Testing d3"
author: "Steve Simon"
date: "2022-06-01"
source: new
categories: 
- Blog post
tags: 
- Graphical display
output: html_document
---
